Dependent Object Types

### 2012-08-31 doc/candidacy/report.tex
typo

We present three papers~\cite{homl,tribe,nuObj}, each of which models
a calculus with path-dependent types.
\begin{itemize}
\item The first paper, {\it A Type-Theoretic Approach to Higher-Order
  Modules with Sharing} by Robert Harper and Mark
  Lillibridge~\cite{homl}, presents a calculus for modules in the ML
  tradition. Path-dependent types arise because modules, which may
  contain type components, are first-class values in their calculus.
\item The second paper, {\it Tribe: a simple virtual class calculus}
  by Dave Clarke, Sophia Drossopoulou, James Noble and Tobias
  Wrigstad~\cite{tribe}, presents a core calculus for virtual
  classes. Path-dependent types arise because, in Tribe, paths are
  types, and, almost vice versa: each type is a generalized form of
  path.
\item The third paper, {\it A Nomial Theory of Objects with Dependent
  Types} by Martin Odersky, Vincent Cremet, Christine R{\"o}ckl and
  Matthias Zenger~\cite{nuObj}, presents a calculus which unifies
  concepts from advanced object-oriented systems and module systems
  and, with~\cite{FS}, serves as a type-theoretic foundation for many
  features of Scala's type system. Path-dependent types arise because
  any path $p$ has a singleton type $p.\type$.
\end{itemize}

>>>>

We present three papers~\cite{homl,tribe,nuObj}, each of which models
a calculus with path-dependent types.
\begin{itemize}
\item The first paper, {\it A Type-Theoretic Approach to Higher-Order
  Modules with Sharing} by Robert Harper and Mark
  Lillibridge~\cite{homl}, presents a calculus for modules in the ML
  tradition. Path-dependent types arise because modules, which may
  contain type components, are first-class values in their calculus.
\item The second paper, {\it Tribe: a simple virtual class calculus}
  by Dave Clarke, Sophia Drossopoulou, James Noble and Tobias
  Wrigstad~\cite{tribe}, presents a core calculus for virtual
  classes. Path-dependent types arise because, in Tribe, paths are
  types, and, almost vice versa: each type is a generalized form of
  path.
\item The third paper, {\it A Nominal Theory of Objects with Dependent
  Types} by Martin Odersky, Vincent Cremet, Christine R{\"o}ckl and
  Matthias Zenger~\cite{nuObj}, presents a calculus which unifies
  concepts from advanced object-oriented systems and module systems
  and, with~\cite{FS}, serves as a type-theoretic foundation for many
  features of Scala's type system. Path-dependent types arise because
  any path $p$ has a singleton type $p.\type$.
\end{itemize}
